Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-07 MUSES_vs_BYOD_solutions.tex
Revert "Adding clarification about MUSES advantages with respect to self-adaptation"
This reverts commit 57850504801b146e170ce68a124da32d4a2314a8.

MUSES is mainly a free, open-source, platform independent solution, and that makes it a very good option in a first comparison against most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also  covers laptops and company PCs too, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.

>>>>

MUSES is mainly a free, open-source, platform independent solution, and adopts the recommended best practices by Romer \cite{Romer14BestPractices}. %Está bien aquí Fergu?
 These features make it a good alternative to most of the proprietary, close and system-specific tools presented in Section \ref{sec:toolsreview} (all but WSO2). In addition, most of the existing tools take into account only smartphones and tablets, but MUSES also covers laptops and company PCs, thus, it is not only for BYOD. Moreover, the companies which might want to work with one of the reviewed systems need a specific operating system in the server (such as Windows Server, for instance), being even more restrictive in some cases. This is specially remarkable in the case of the Blackphone, forcing the companies and the employees to purchase a specific device. MUSES is a good solution towards these cases, since it is a multiplatform system in both the client and the server.
